---
title: "Definitions:"
site: 
  distill::distill_website:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = '/Users/Serena/Desktop/Summer Research Documents/')

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}

library(sp)
library(rgeos)
library(rgdal)
library(leaflet)

n <- read.csv("New Data/Cleaned All/Classify Data/Classify Neighborhoods Fluid2.csv", header = TRUE, as.is = TRUE)

pitt <- readOGR("GIS/Pittsburgh ShapeFiles/Pitt_censustracts2/pitt_censustracts2.shp")
par(mar = c(5,6,3,6)) #original margins 

#merging
pitt <- merge(pitt, n, by.y = "tract", by.x = "NAME")

```

```{r}
############################################################################################

tract.gentrifiable <- n$tract[which(n$gentrifiable==1)]

#DEFINITION 1
def1.neighborhoods <- n$neighborhood[which(n$def1.gentrifying==1)]
tract.gentrifiable <- n$tract[which(n$gentrifiable==1)]
def1.tract.gent <- n$tract[which(n$def1.gentrifying==1)]
def1.tract.na <- n$tract[which(is.na(n$def1.gentrifying))]

#DEFINITION 2 
def2.neighborhoods <- n$neighborhood[which(n$def2.gentrifying==1)]
def2.tract.gent <- n$tract[which(n$def2.gentrifying==1)]
def2.tract.na <- n$tract[which(is.na(n$def2.gentrifying))]

#DEFINITION 3
def3.neighborhoods <- n$neighborhood[which(n$def3.gentrifying==1)]
def3.tract.gent <- n$tract[which(n$def3.gentrifying==1)]
def3.tract.na <- n$tract[which(is.na(n$def3.gentrifying))]

#DEFINITION 4 - Increasing
def4.neighborhoods <- n$neighborhood[which(n$def4.gentrifying==1)]
def4.tract.gent <- n$tract[which(n$def4.gentrifying==1)]
def4.tract.na <- n$tract[which(is.na(n$def4.gentrifying))]

#DEFINITION 4 - Decreasing
def4.neighborhoods2 <- n$neighborhood[which(n$def4.gentrifying2==1)]
def4.tract.gent2 <- n$tract[which(n$def4.gentrifying2==1)]
def4.tract.na2 <- n$tract[which(is.na(n$def4.gentrifying2))]

#DEFINITION 5 - Increasing
def5.neighborhoods <- n$neighborhood[which(n$def5.gentrifying==1)]
def5.tract.gent <- n$tract[which(n$def5.gentrifying==1)]
def5.tract.na <- n$tract[which(is.na(n$def5.gentrifying))]

#DEFINITION 5 - Decreasing
def5.neighborhoods2 <- n$neighborhood[which(n$def5.gentrifying2==1)]
def5.tract.gent2 <- n$tract[which(n$def5.gentrifying2==1)]
def5.tract.na2 <- n$tract[which(is.na(n$def5.gentrifying2))]

#DEFINITION 6 - Increasing
def6.neighborhoods <- n$neighborhood[which(n$def6.gentrifying==1)]
def6.tract.gent <- n$tract[which(n$def6.gentrifying==1)]
def6.tract.na <- n$tract[which(is.na(n$def6.gentrifying))]

#DEFINITION 6 - Decreasing
def6.neighborhoods2 <- n$neighborhood[which(n$def6.gentrifying2==1)]
def6.tract.gent2 <- n$tract[which(n$def6.gentrifying2==1)]
def6.tract.na2 <- n$tract[which(is.na(n$def6.gentrifying2))]

#DEFINITION 7
def7.neighborhoods <- n$neighborhood[which(n$def7.gentrifying==1)]
def7.tract.gent <- n$tract[which(n$def7.gentrifying==1)]
def7.tract.na <- n$tract[which(is.na(n$def7.gentrifying))]

#DEFINITION 8
def8.neighborhoods <- n$neighborhood[which(n$def8.gentrifying==1)]
def8.tract.gent <- n$tract[which(n$def8.gentrifying==1)]
def8.tract.na <- n$tract[which(is.na(n$def8.gentrifying))]

#DEFINITION 9
def9.neighborhoods <- n$neighborhood[which(n$def9.gentrifying==1)]
def9.tract.gent <- n$tract[which(n$def9.gentrifying==1)]
def9.tract.na <- n$tract[which(is.na(n$def9.gentrifying))]

#DEFINITION 10 - Increasing 
def10.neighborhoods <- n$neighborhood[which(n$def10.gentrifying==1)]
def10.tract.gent <- n$tract[which(n$def10.gentrifying==1)]
def10.tract.na <- n$tract[which(is.na(n$def10.gentrifying))]

#DEFINITION 10 - Decreasing 
def10.neighborhoods2 <- n$neighborhood[which(n$def10.gentrifying2==1)]
def10.tract.gent2 <- n$tract[which(n$def10.gentrifying2==1)]
def10.tract.na2 <- n$tract[which(is.na(n$def10.gentrifying2))]

#DEFINITION 11 - Increasing 
def11.neighborhoods <- n$neighborhood[which(n$def11.gentrifying==1)]
def11.tract.gent <- n$tract[which(n$def11.gentrifying==1)]
def11.tract.na <- n$tract[which(is.na(n$def11.gentrifying))]

#DEFINITION 11 - Decreasing 
def11.neighborhoods2 <- n$neighborhood[which(n$def11.gentrifying2==1)]
def11.tract.gent2 <- n$tract[which(n$def11.gentrifying2==1)]
def11.tract.na2 <- n$tract[which(is.na(n$def11.gentrifying2))]

#DEFINITION 12 - Increasing 
def12.neighborhoods <- n$neighborhood[which(n$def12.gentrifying==1)]
def12.tract.gent <- n$tract[which(n$def12.gentrifying==1)]
def12.tract.na <- n$tract[which(is.na(n$def12.gentrifying))]

#DEFINITION 12 - Decreasing 
def12.neighborhoods2 <- n$neighborhood[which(n$def12.gentrifying2==1)]
def12.tract.gent2 <- n$tract[which(n$def12.gentrifying2==1)]
def12.tract.na2 <- n$tract[which(is.na(n$def12.gentrifying2))]

############################################################################################### 

#CREATING THE LISTS OF LISTS 
#Fluid Definition 
gentrifying.locations <- list(def1.tract.gent, def1.neighborhoods, def2.tract.gent,
                              def2.neighborhoods, def3.tract.gent, def3.neighborhoods,
                              def4.tract.gent, def4.neighborhoods, def5.tract.gent,
                              def5.neighborhoods, def6.tract.gent, def6.neighborhoods,
                              def7.tract.gent, def7.neighborhoods, def8.tract.gent,
                              def8.neighborhoods, def9.tract.gent, def9.neighborhoods,
                              def10.tract.gent, def10.neighborhoods, def11.tract.gent,
                              def11.neighborhoods,def12.tract.gent, def12.neighborhoods)
names(gentrifying.locations) <- c("definition 1", "definition 1b", "definition 2", 
                                  "definition 2b","definition 3", "definition 3b", 
                                  "definition 4", "definition 4b","definition 5", 
                                  "definition 5b", "definition 6", "definition 6b",
                                  "definition 7", "definition 7b", "definition 8", 
                                  "definition 11", "definition 11b", "definition 12",
                                  "definition 12b")

gentrifying.locations2 <- list(def4.tract.gent2, def4.neighborhoods2, def5.tract.gent2, 
                               def5.neighborhoods2, def6.tract.gent2, def6.neighborhoods2,
                               def10.tract.gent2, def10.neighborhoods2, def11.tract.gent2,
                               def11.neighborhoods2, def12.tract.gent2, def12.neighborhoods2)
names(gentrifying.locations2) <- c("definition 4", "definition 4b", "definition 5", 
                                   "definition 5b", "definition 6", "definition 6b",
                                   "definition 10", "definition 10b", "definition 11",
                                   "definition 11b", "definition 12", "definition 12b")

```

# Definition 1

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Home Value > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase

```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def1.tract.gent)){
  plot(pitt[pitt$NAME == def1.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def1.tract.na)){
  plot(pitt[pitt$NAME == def1.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```
    
Gentrifying Tracts: 
603, 809, 901, 903, 1011, 1113, 1115, 1915, 2107, 2406, 2509, 2614, 2703, 5623, 5632


# Definition 2

Variables: 

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase
    
```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def2.tract.gent)){
  plot(pitt[pitt$NAME == def2.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def2.tract.na)){
  plot(pitt[pitt$NAME == def2.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```

Gentrifying Tracts:
603, 809, 901, 903, 1011, 1114, 1115, 2107, 2406, 2509, 2609, 2901, 5630, 5632 

        
# Definition 3

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Home Value or Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def3.tract.gent)){
  plot(pitt[pitt$NAME == def3.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def3.tract.na)){
  plot(pitt[pitt$NAME == def3.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```

Gentrifying Tracts: 603, 809, 901, 903, 1011, 1115, 2107, 2406, 2509, 2609, 5632

               
# Definition 4
    
### Increasing 


Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % proportion increase in Vacancy > citywide median % increase

- % increase in median Home Value > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def4.tract.gent)){
  plot(pitt[pitt$NAME == def4.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def4.tract.na)){
  plot(pitt[pitt$NAME == def4.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```

Gentrifying Tracts: 901, 1011, 1113, 2107, 2614, 5632
               

### Decreasing  


Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % proportion increase in Vacancy < citywide median % increase

- % increase in median Home Value > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def4.tract.gent)){
  plot(pitt[pitt$NAME == def4.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def4.tract.na)){
  plot(pitt[pitt$NAME == def4.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```

Gentrifying Tracts: 603, 809, 903, 1115, 1915, 2406, 2509, 2703, 562               


# Definition 5

### Increasing 


Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % proportion increase in Vacancy > citywide median % increase

- % increase in median Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def5.tract.gent)){
  plot(pitt[pitt$NAME == def5.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def5.tract.na)){
  plot(pitt[pitt$NAME == def5.tract.na[i], ], col="grey", add=T)
}

#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```

Gentrifying Tracts: 901, 1011, 2107, 2609, 5630, 5632
               

### Decreasing  

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % proportion increase in Vacancy < citywide median % increase

- % increase in median Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def5.tract.gent)){
  plot(pitt[pitt$NAME == def5.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def5.tract.na)){
  plot(pitt[pitt$NAME == def5.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```
         
Gentrifying Tracts: 603, 809, 903, 1114, 1115, 2406, 2509, 2901      
     

# Definition 6

### Increasing


Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % proportion increase in Vacancy > citywide median % increase

- % increase in median Home Value or Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def6.tract.gent)){
  plot(pitt[pitt$NAME == def6.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def6.tract.na)){
  plot(pitt[pitt$NAME == def6.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```

Gentrifying Tracts: 901, 1011, 2107, 2609, 5632


### Decreasing

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % proportion increase in Vacancy < citywide median % increase

- % increase in median Home Value or Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def6.tract.gent)){
  plot(pitt[pitt$NAME == def6.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def6.tract.na)){
  plot(pitt[pitt$NAME == def6.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)


```

Gentrifying Tracts: 603, 809, 903, 1115, 2406, 2509


# Definition 7

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income", 

- % increase in median Household Income > citywide median % increase", 

- % increase in median Home Value > citywide median % increase",

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def7.tract.gent)){
  plot(pitt[pitt$NAME == def7.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def7.tract.na)){
  plot(pitt[pitt$NAME == def7.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```

Gentrifying Tracts: 603, 809, 901, 903, 1011, 1113, 1115, 1915, 2107, 2406, 2614, 2703, 5632


# Definition 8

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % increase in median Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def8.tract.gent)){
  plot(pitt[pitt$NAME == def8.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def8.tract.na)){
  plot(pitt[pitt$NAME == def8.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```

Gentrifying Tracts: 603, 809, 901, 903, 1011, 1114, 1115, 2107, 2406, 5630, 5632


# Definition 9

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % increase in median Home Value or Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def9.tract.gent)){
  plot(pitt[pitt$NAME == def9.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def9.tract.na)){
  plot(pitt[pitt$NAME == def9.tract.na[i], ], col="grey", add=T)
}

#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```

Gentrifying Tracts: 603, 809, 901, 903, 1011, 1115, 2107, 2406, 5632


# Definition 10

### Increasing 

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % proportion increase in Vacancy > citywide median % increase

- % increase in median Home Value > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def10.tract.gent)){
  plot(pitt[pitt$NAME == def10.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def10.tract.na)){
  plot(pitt[pitt$NAME == def10.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```

Gentrifying Tracts: 901, 1011, 1113, 2107, 2614, 5632


### Decreasing 

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % proportion increase in Vacancy < citywide median % increase

- % increase in median Home Value > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def10.tract.gent)){
  plot(pitt[pitt$NAME == def10.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def10.tract.na)){
  plot(pitt[pitt$NAME == def10.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```

Gentrifying Tracts: 603, 809, 903, 1115, 1915, 2406, 2703


# Definition 11

### Increasing 

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % proportion increase in Vacancy > citywide median % increase

- % increase in median Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def11.tract.gent)){
  plot(pitt[pitt$NAME == def11.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def11.tract.na)){
  plot(pitt[pitt$NAME == def11.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```
           
Gentrifying Tracts: 901, 1011, 2107, 5630, 5632


#### Decreasing 

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % proportion increase in Vacancy < citywide median % increase

- % increase in median Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def11.tract.gent)){
  plot(pitt[pitt$NAME == def11.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def11.tract.na)){
  plot(pitt[pitt$NAME == def11.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```
               
Gentrifying Tracts: 603, 809, 903, 1114, 1115, 2406               
               

# Definition 12

### Increasing 
  
Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % proportion increase in Vacancy > citywide median % increase
               
- % increase in median Home Value or Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def12.tract.gent)){
  plot(pitt[pitt$NAME == def12.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def12.tract.na)){
  plot(pitt[pitt$NAME == def12.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```

Gentrifying Tracts: 901, 1011, 2107, 5632
              

### Decreasing 
  
Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % proportion increase in Vacancy < citywide median % increase
               
- % increase in median Home Value or Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=6}

plot(pitt)
plot(pitt, col="skyblue", add = TRUE)
#color def tracts orange
for(i in 1:length(tract.gentrifiable)){
  plot(pitt[pitt$NAME == tract.gentrifiable[i], ], col="dark grey", add=T)
}
for(i in 1:length(def12.tract.gent)){
  plot(pitt[pitt$NAME == def12.tract.gent[i], ], col="orange", add=T)
}
for(i in 1:length(def12.tract.na)){
  plot(pitt[pitt$NAME == def12.tract.na[i], ], col="grey", add=T)
}
#Key
mtext("Gentrifying", side = 1, adj = 0, line = 1, col = "orange", cex = 0.85)
mtext("Gentrifiable Non-Gentrifying", side = 1, adj = 0, line = 2, col = "gray 44", cex = 0.85)
mtext("Non-Gentrifying", side = 1, adj = 0, line = 3, col = "deepskyblue", cex = 0.85)
mtext("Tract Data Missing", side = 1, adj = 0, line = 0, col = "dark grey", cex = 0.85)

```

Gentrifying Tracts: 603, 809, 903, 1115, 2406
