---
title: "Definitions:"
output: html_document
site: 
  distill::distill_website:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = '/Users/Serena/Desktop/Summer Research Documents/')

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}

library(sp)
library(rgeos)
library(rgdal)
library(leaflet)

n <- read.csv("New Data/Cleaned All/Classify Data/Classify_all.csv", header = TRUE, as.is = TRUE)

pitt <- readOGR("GIS/Pittsburgh ShapeFiles/Pitt_censustracts2/pitt_censustracts2.shp")
par(mar = c(5,6,3,6)) #original margins 

#merging
pitt <- merge(pitt, n, by.y = "tract", by.x = "NAME")

```


```{r}
############################################################################################

tract.gentrifiable <- n$tract[which(n$gentrifiable==1)]

#DEFINITION 1
def1.neighborhoods <- n$neighborhood[which(n$def1.gentrifying==1)]
tract.gentrifiable <- n$tract[which(n$gentrifiable==1)]
def1.tract.gent <- n$tract[which(n$def1.gentrifying==1)]
def1.tract.na <- n$tract[which(is.na(n$def1.gentrifying))]

#DEFINITION 2 
def2.neighborhoods <- n$neighborhood[which(n$def2.gentrifying==1)]
def2.tract.gent <- n$tract[which(n$def2.gentrifying==1)]
def2.tract.na <- n$tract[which(is.na(n$def2.gentrifying))]

#DEFINITION 3
def3.neighborhoods.both <- n$neighborhood[which(n$def3.gentrifying.both==1)]
def3.neighborhoods.or <- n$neighborhood[which(n$def3.gentrifying.or==1)]

def3.tract.gent.both <- n$tract[which(n$def3.gentrifying.both==1)]
def3.tract.gent.or <- n$tract[which(n$def3.gentrifying.or==1)]

def3.tract.na.both <- n$tract[which(is.na(n$def3.gentrifying.both))]
def3.tract.na.or <- n$tract[which(is.na(n$def3.gentrifying.or))]

#DEFINITION 4 - Increasing
def4.neighborhoods.i <- n$neighborhood[which(n$def4.gentrifying==1)]
def4.tract.gent.i <- n$tract[which(n$def4.gentrifying==1)]
def4.tract.na.i <- n$tract[which(is.na(n$def4.gentrifying))]

#DEFINITION 4 - Decreasing
def4.neighborhoods.d <- n$neighborhood[which(n$def4.gentrifying2==1)]
def4.tract.gent.d <- n$tract[which(n$def4.gentrifying2==1)]
def4.tract.na.d <- n$tract[which(is.na(n$def4.gentrifying2))]

#DEFINITION 5 - Increasing
def5.neighborhoods.i <- n$neighborhood[which(n$def5.gentrifying==1)]
def5.tract.gent.i <- n$tract[which(n$def5.gentrifying==1)]
def5.tract.na.i <- n$tract[which(is.na(n$def5.gentrifying))]

#DEFINITION 5 - Decreasing
def5.neighborhoods.d <- n$neighborhood[which(n$def5.gentrifying2==1)]
def5.tract.gent.d <- n$tract[which(n$def5.gentrifying2==1)]
def5.tract.na.d <- n$tract[which(is.na(n$def5.gentrifying2))]

#DEFINITION 6 - Increasing/Both
def6.neighborhoods.i.both <- n$neighborhood[which(n$def6.gentrifying.both==1)]
def6.tract.gent.i.both <- n$tract[which(n$def6.gentrifying.both==1)]
def6.tract.na.i.both <- n$tract[which(is.na(n$def6.gentrifying.both))]

#DEFINITION 6 - Decreasing/Both
def6.neighborhoods.d.both <- n$neighborhood[which(n$def6.gentrifying2.both==1)]
def6.tract.gent.d.both <- n$tract[which(n$def6.gentrifying2.both==1)]
def6.tract.na.d.both <- n$tract[which(is.na(n$def6.gentrifying2.both))]

#DEFINITION 6 - Increasing/Or
def6.neighborhoods.i.or <- n$neighborhood[which(n$def6.gentrifying.or==1)]
def6.tract.gent.i.or <- n$tract[which(n$def6.gentrifying.or==1)]
def6.tract.na.i.or <- n$tract[which(is.na(n$def6.gentrifying.or))]

#DEFINITION 6 - Decreasing/Or
def6.neighborhoods.d.or <- n$neighborhood[which(n$def6.gentrifying2.or==1)]
def6.tract.gent.d.or <- n$tract[which(n$def6.gentrifying2.or==1)]
def6.tract.na.d.or <- n$tract[which(is.na(n$def6.gentrifying2.or))]

#DEFINITION 7
def7.neighborhoods <- n$neighborhood[which(n$def7.gentrifying==1)]
def7.tract.gent <- n$tract[which(n$def7.gentrifying==1)]
def7.tract.na <- n$tract[which(is.na(n$def7.gentrifying))]

#DEFINITION 8
def8.neighborhoods <- n$neighborhood[which(n$def8.gentrifying==1)]
def8.tract.gent <- n$tract[which(n$def8.gentrifying==1)]
def8.tract.na <- n$tract[which(is.na(n$def8.gentrifying))]

#DEFINITION 9 - Both
def9.neighborhoods.both <- n$neighborhood[which(n$def9.gentrifying.both==1)]
def9.tract.gent.both <- n$tract[which(n$def9.gentrifying.both==1)]
def9.tract.na.both <- n$tract[which(is.na(n$def9.gentrifying.both))]

#DEFINITION 9 - Or
def9.neighborhoods.or <- n$neighborhood[which(n$def9.gentrifying.or==1)]
def9.tract.gent.or <- n$tract[which(n$def9.gentrifying.or==1)]
def9.tract.na.or <- n$tract[which(is.na(n$def9.gentrifying.or))]

#DEFINITION 10 - Increasing 
def10.neighborhoods.i <- n$neighborhood[which(n$def10.gentrifying==1)]
def10.tract.gent.i <- n$tract[which(n$def10.gentrifying==1)]
def10.tract.na.i <- n$tract[which(is.na(n$def10.gentrifying))]

#DEFINITION 10 - Decreasing  
def10.neighborhoods.d <- n$neighborhood[which(n$def10.gentrifying2==1)]
def10.tract.gent.d <- n$tract[which(n$def10.gentrifying2==1)]
def10.tract.na.d <- n$tract[which(is.na(n$def10.gentrifying2))]

#DEFINITION 11 - Increasing 
def11.neighborhoods.i <- n$neighborhood[which(n$def11.gentrifying==1)]
def11.tract.gent.i <- n$tract[which(n$def11.gentrifying==1)]
def11.tract.na.i <- n$tract[which(is.na(n$def11.gentrifying))]

#DEFINITION 11 - Decreasing 
def11.neighborhoods.d <- n$neighborhood[which(n$def11.gentrifying2==1)]
def11.tract.gent.d <- n$tract[which(n$def11.gentrifying2==1)]
def11.tract.na.d <- n$tract[which(is.na(n$def11.gentrifying2))]

#DEFINITION 12 - Increasing/Both
def12.neighborhoods.i.both <- n$neighborhood[which(n$def12.gentrifying.both==1)]
def12.tract.gent.i.both <- n$tract[which(n$def12.gentrifying.both==1)]
def12.tract.na.i.both <- n$tract[which(is.na(n$def12.gentrifying.both))]

#DEFINITION 12 - Decreasing/Both
def12.neighborhoods.d.both <- n$neighborhood[which(n$def12.gentrifying2.both==1)]
def12.tract.gent.d.both <- n$tract[which(n$def12.gentrifying2.both==1)]
def12.tract.na.d.both <- n$tract[which(is.na(n$def12.gentrifying2.both))]

#DEFINITION 12 - Increasing/Or
def12.neighborhoods.i.or <- n$neighborhood[which(n$def12.gentrifying.or==1)]
def12.tract.gent.i.or <- n$tract[which(n$def12.gentrifying.or==1)]
def12.tract.na.i.or <- n$tract[which(is.na(n$def12.gentrifying.or))]

#DEFINITION 12 - Decreasing/Or
def12.neighborhoods.d.or <- n$neighborhood[which(n$def12.gentrifying2.or==1)]
def12.tract.gent.d.or <- n$tract[which(n$def12.gentrifying2.or==1)]
def12.tract.na.d.or <- n$tract[which(is.na(n$def12.gentrifying2.or))]

############################################################################################### 

#CREATING THE LISTS OF LISTS 
#Fluid Definition 
gentrifying.locations <- list(def1.tract.gent, def1.neighborhoods, 
                              def2.tract.gent, def2.neighborhoods,
                              def3.tract.gent.both, def3.neighborhoods.both, 
                              def3.tract.gent.or, def3.neighborhoods.or,
                              def4.tract.gent.i, def4.neighborhoods.i, 
                              def4.tract.gent.d, def4.neighborhoods.d,
                              def5.tract.gent.i, def5.neighborhoods.i, 
                              def5.tract.gent.d, def5.neighborhoods.d,
                              def6.tract.gent.i.both, def6.neighborhoods.i.both, 
                              def6.tract.gent.d.both, def6.neighborhoods.d.both,
                              def6.tract.gent.i.or, def6.neighborhoods.i.or, 
                              def6.tract.gent.d.or, def6.neighborhoods.d.or,
                              def7.tract.gent, def7.neighborhoods, 
                              def8.tract.gent, def8.neighborhoods,
                              def9.tract.gent.both, def9.neighborhoods.both, 
                              def9.tract.gent.or, def9.neighborhoods.or, 
                              def10.tract.gent.i, def10.neighborhoods.i, 
                              def10.tract.gent.d, def10.neighborhoods.d,
                              def11.tract.gent.i, def11.neighborhoods.i, 
                              def11.tract.gent.d, def11.neighborhoods.d,
                              def12.tract.gent.i.both, def12.neighborhoods.i.both, 
                              def12.tract.gent.d.both, def12.neighborhoods.d.both,
                              def12.tract.gent.i.or, def12.neighborhoods.i.or, 
                              def12.tract.gent.d.or, def12.neighborhoods.d.or)

names(gentrifying.locations) <- c("D1", "N1", 
                                  "D2", "N2",
                                  "D3 Both", "N3 Both", "D3 Or", "N3 Or",
                                  "D4 Inc", "N4 Inc", "D4 Dec", "N4 Dec",
                                  "D5 Inc", "N5 Inc", "D5 Dec", "N5 Dec",
                                  "D6 Inc/Both", "N6 Inc/Both", "D6 Dec/Both", "N6 Dec/Both", 
                                  "D6 Inc/Or", "N6 Inc/Or", "D6 Dec/Or", "N6 Dec/Or",
                                  "D7", "N7", 
                                  "D8", "N8",
                                  "D9 Both", "N9 Both", "D9 Or", "N9 Or", 
                                  "D10 Inc", "N10 Inc", "D10 Dec", "N10 Dec",
                                  "D11 Inc", "N11 Inc", "D11 Dec", "N11 Dec", 
                                  "D12 Inc/Both", "N12 Inc/Both", "D12 Dec/Both", "N12 Dec/Both", 
                                  "D12 Inc/Or", "N12 Inc/Or", "D12 Dec/Or", "N12 Dec/Or")

```


## Definition 1

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Home Value > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase

```{r, fig.height=6, fig.width=12}
# Adding in the interactive maps
my.col <- rep("slategrey", 137)
my.col[pitt$def1.gentrifying == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def1.gentrifying == 1] <- "orange"
def1.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 1",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def1.int

```
    
Gentrifying Tracts: 
603, 809, 901, 903, 1011, 1113, 1115, 1915, 2107, 2406, 2509, 2614, 2703, 5623, 5632




## Definition 2

Variables: 

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase
    
```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def2.gentrifying == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def2.gentrifying == 1] <- "orange"
def2.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 2",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def2.int

```

Gentrifying Tracts:
603, 809, 901, 903, 1011, 1114, 1115, 2107, 2406, 2509, 2609, 2901, 5630, 5632 

        


## Definition 3

### - Home Value & Rent

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Home Value & Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def3.gentrifying.both == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def3.gentrifying.both == 1] <- "orange"
def3.int.b <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 3",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def3.int.b

```

Gentrifying Tracts: 603, 809, 901, 903, 1011, 1115, 2107, 2406, 2509, 2609, 5632

### - Home Value or Rent

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Home Value or Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def3.gentrifying.or == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def3.gentrifying.or == 1] <- "orange"
def3.int.o <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 3",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def3.int.o

```

Gentrifying Tracts:  603, 809, 901, 903, 1011, 1113, 1114, 1115, 1915, 2107, 2406, 2509, 2609, 2614, 2703, 2901, 5623, 5630, 5632

               


## Definition 4


Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % proportion increase in Vacancy < citywide median % increase

- % increase in median Home Value > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def4.gentrifying2 == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def4.gentrifying2 == 1] <- "orange"
def4.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 4",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def4.int

```

Gentrifying Tracts: 603, 809, 903, 1115, 1915, 2406, 2509, 2703, 5623               




## Definition 5

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % proportion increase in Vacancy < citywide median % increase

- % increase in median Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def5.gentrifying2 == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def5.gentrifying2 == 1] <- "orange"
def5.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 5",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def5.int

```
         
Gentrifying Tracts: 603, 809, 903, 1114, 1115, 2406, 2509, 2901      
     



## Definition 6

### - Home Value & Rent 


Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % proportion increase in Vacancy < citywide median % increase

- % increase in median Home Value & Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def6.gentrifying2.both == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def6.gentrifying2.both == 1] <- "orange"
def6.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 6",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def6.int

```

Gentrifying Tracts: 603, 809, 903, 1115, 2406, 2509


### - Home Value or Rent

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % proportion increase in Vacancy < citywide median % increase

- % increase in median Home Value or Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def6.gentrifying2.or == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def6.gentrifying2.or == 1] <- "orange"
def6.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 6",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def6.int

```

Gentrifying Tracts: 603, 809, 903, 1114, 1115, 1915, 2406, 2509, 2703, 2901, 5623




## Definition 7

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income", 

- % increase in median Household Income > citywide median % increase", 

- % increase in median Home Value > citywide median % increase",

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def7.gentrifying == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def7.gentrifying == 1] <- "orange"
def7.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 7",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def7.int

```

Gentrifying Tracts: 603, 809, 901, 903, 1011, 1113, 1115, 1915, 2107, 2406, 2614, 2703, 5632




## Definition 8

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % increase in median Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def8.gentrifying == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def8.gentrifying == 1] <- "orange"
def8.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 8",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def8.int

```

Gentrifying Tracts: 603, 809, 901, 903, 1011, 1114, 1115, 2107, 2406, 5630, 5632




## Definition 9

### - Home Value & Rent

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % increase in median Home Value & Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def9.gentrifying.both == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def9.gentrifying.both == 1] <- "orange"
def9.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 9",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def9.int

```

Gentrifying Tracts: 603, 809, 901, 903, 1011, 1115, 2107, 2406, 5632


### - Home Value or Rent

Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % increase in median Home Value or Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def9.gentrifying.or == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def9.gentrifying.or == 1] <- "orange"
def9.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 9",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def9.int

```

Gentrifying Tracts: 603, 809, 901, 903, 1011, 1113, 1114, 1115, 1915, 2107, 2406, 2614, 2703, 5630, 5632




## Definition 10


Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % proportion increase in Vacancy < citywide median % increase

- % increase in median Home Value > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def10.gentrifying2 == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def10.gentrifying2 == 1] <- "orange"
def10.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 10",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def10.int

```

Gentrifying Tracts: 603, 809, 903, 1115, 1915, 2406, 2703




## Definition 11


Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % proportion increase in Vacancy < citywide median % increase

- % increase in median Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def11.gentrifying2 == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def11.gentrifying2 == 1] <- "orange"
def11.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 11",
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def11.int

```
               
Gentrifying Tracts: 603, 809, 903, 1114, 1115, 2406               
               







## Definition 12


### - Home Value & Rent 
  
Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % proportion increase in Vacancy < citywide median % increase
               
- % increase in median Home Value & Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def12.gentrifying2.both == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def12.gentrifying2.both == 1] <- "orange"
def12.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 12", 
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def12.int

```

Gentrifying Tracts: 603, 809, 903, 1115, 2406


### - Home Value or Rent 
  
Variables:

- 2010 tract median Household Income < 2010 citywide median Household Income

- % increase in median Household Income > citywide median % increase

- % proportion increase in Vacancy < citywide median % increase
               
- % increase in median Home Value or Rent > citywide median % increase

- % increase in proportion of Bachelor's Degree and above > citywide median % increase


```{r, fig.height=6, fig.width=12}

my.col <- rep("slategrey", 137)
my.col[pitt$def12.gentrifying2.or == 0] <- "skyblue"
my.col[pitt$gentrifiable == 1] <- "powderblue"
my.col[pitt$def12.gentrifying2.or == 1] <- "orange"
def12.int <- leaflet(pitt) %>%
  addPolygons(
    label=paste("Tract:", pitt$NAME, "Neighborhood:", pitt$neighborhood),
    labelOptions= labelOptions(direction = 'auto'),
    weight=0.5, color = "black", opacity=1, fillOpacity = 0.7, fillColor = my.col
  ) %>%
  addLegend(
    title = "Definition 12", 
    position = c("bottomleft"),
    colors = c("orange", "skyblue", "powderblue", "slategrey"),
    labels = c("Gentrifying", "Non-Gentrifying", "Gentrifiable Non-Gentrifying", "Tract Data Missing")
  )
def12.int

```

Gentrifying Tracts: 603, 809, 903, 1114, 1115, 1915, 2406, 2703




